### 2021-03-24 exploratory/2021/test_criteria.Rmd
Select seed col

```{r read}
dat <- read_tsv(here('subworkflows', '3_fit_sample_split', 'results', 
                     'optifit_crit_check.tsv')) %>% 
  mutate_perf() %>% 
  select(dataset, printref, criteria, mcc, fraction_mapped, sec, mem_gb) 
```

>>>>

```{r read}
dat <- read_tsv(here('subworkflows', '3_fit_sample_split', 'results', 
                     'optifit_crit_check.tsv')) %>% 
  mutate_perf() %>% 
  select(dataset, printref, criteria, mcc, fraction_mapped, sec, mem_gb, seed) 
```
